Homework 1 - Team 1
========================================================

### Task 0 - Load the data

```{r}
suppressMessages(library(dplyr))
load("lego_sales.RData")
```

### Task 1 - Tidying the data

Intialize the Data Frame
```{r}
# find top level names
name0 = sales %>% unlist(recursive=FALSE) %>% names() %>% unique()

# identify number of rows based on maxiumum number of each catagory
sum_n = 
    sapply(name0, function(x) 
        sapply(sales, function(y) 
            length(y[[x]]))) %>% 
    colSums()

# identify subcatagory names
cat_name = 
    sapply(name0, function(x)
        sapply(sales, function(y)
            y[[x]] %>% 
            unlist() %>%
            names()) %>%
        unlist() %>% 
        unique()) 

# create list of column names
cat_name = cat_name[!(sapply(cat_name, is.null))]
name = c(name0, unlist(cat_name, use.names = FALSE))
    
# intialize the data frame given the extents discovered above
lego_df = matrix(nrow = max(sum_n), ncol = length(name)) %>%
    data.frame() %>% 
    tbl_df() %>%
    setNames(name)

# hobbies is a special case
lego_df['hobbies'] = as.list(lego_df['hobbies'])
```

Create a helper function
```{r}
# A 'safe' rep function that returns NA value when encountering NULL
# Outputs a list if the input is a vector with multiple elements
rep_safe = function(x, t) {
    if (is.null(x) | is.list(x)) {
        rep(NA, t) 
    } else if (length(x) != 1) {
        list(x)[rep(1,t)]
    } else {
        rep(x, t)
    }
}
```

Loop over and fill the data frame
```{r}
name_max = names(which.max(sum_n))
for (n in name0) {
    lego_df[[n]] = 
        sapply(sales, function(x) 
            rep_safe(x[[n]], length(x[[name_max]]))) %>%
        unlist(recursive=FALSE)
    for (c in cat_name[[n]]) {
        lego_df[[c]] =
            sapply(sales, function(x) 
                sapply(x[[n]], function(y) y[[c]]))  %>% 
            unlist()
    }
}
```

Finally we need to do some manual tidy-ing: 1) in 'hobbies', replace "length = 0"" with "NA"
2) delete the column "purchases" since all the information in the purchases are already in the other columns. 
```{r}
is_missing = sapply(lego_df[['hobbies']], function(x) length(x) == 0)
lego_df[['hobbies']][which(is_missing)] = list(NA)
lego_df['purchases'] = NULL
```



## Task 2 - Processing the data

###1. What was the most common first name of purchasers? Last name?

After creating the dataframe, we can use dplyr to manipulate the dataframe. We count the unique names in the dataset by *distinct ()* and found out that **Jacob** and **Brown** are the most common first and last names, respectively. 
```{r}
lego_df %>%
    select(first_name, last_name) %>%
    distinct() %>%
    count(first_name, sort = TRUE) %>%
    .[1,1]

lego_df %>%
    select(first_name, last_name) %>%
    distinct() %>%
    count(last_name, sort = TRUE) %>%
    .[1,1]
```

###2. What are the five most popular lego sets based on these data?

Again we use dplyr to manipulate the dataset. Multiple people can purchase the same lego set. Therefore need to group by name of the lego set and then sum up the quantity purchased by different customers. We arrange the summary table in a descending order by quantity and use *slice()* to select the top 5 rows. **Campsite Scrapbook, Ninjago Party Set, Arctic, Daisy's Beauty Salon and Finn** are the five most popular lego sets we found.
```{r}
lego_df %>%
    select(Name, Quantity) %>%
    group_by(Name) %>%
    summarize(Quant_by_name = sum(Quantity)) %>%
    arrange(desc(Quant_by_name)) %>%
    slice(1:5)
```

###3. Which five customers have spent the most money so far and how much have they spent?

We again use dplyr on the dataframe. We use *mutate()* to create a new variable Spent as a product of price and quantity. Using the similar idea in **2)**, we arrange Spent in a descending order and slice the top 5 rows to get the results. Note that after creating the new variable, we need to repipe the dataframe by selecting less variables (replacing Spent with USPrice and Quantity). 
```{r}
lego_df %>% 
    select(first_name, last_name, USPrice, Quantity) %>%
    mutate(Spent = USPrice * Quantity) %>%
    arrange(desc(Spent)) %>%
    select(first_name, last_name, Spent) %>%
    slice(1:5)
```

###4. Which lego theme has made the most money for lego?

The idea of **4)** is the same as **3)** except for an extra grouping process (using *group_by(Theme)* ) after creating the variable. Then the number of row of datasets is reduced and we need to summarize the dataframe before ordering. **Star Wars, Ninjiago, City, Nexo Knights and Minecraft** are summarized as the top 5 themes. 
```{r}
 lego_df %>% 
     select(first_name, last_name, Theme, USPrice, Quantity) %>%
     mutate(Spent = USPrice * Quantity) %>%
     group_by(Theme) %>%
     summarize(Sum_spent = sum(Spent)) %>%
     arrange(desc(Sum_spent)) %>%
     slice(1:5)
```

###5. Do men or women buy more lego sets (per person) on average?

Grouping by gender we found that male on average buy slightly more lego sets than female. However the difference is almost negligible and more tests should be conducted.
```{r}
lego_df %>%
    select(gender, Quantity) %>%
    group_by(gender) %>%
    summarize(mean(Quantity))
```



###6. What are the five most popular hobbies of lego purchasers?

Looping over each individual's *hobbies* in *sales* we can get a table of everyone's hbbies. After manually sorting we found that slicing the top 12 rows will give us the result. Note that all hobbies tied No.4 are considered among the five most popular hobbies. 
```{r}
# easy way: using a table 
a = c()
for(i in 1:length(sales)){
  a = c(sales[[i]]$hobbies, a)
}
sort(table(a), decreasing=T)[1:13] 



# using dplyr:

```

###7. How many total pieces have been purchased from lego by these customers?

We use *transmute()* to create new tibble *Total_Prices* from existing columns of *Pieces* and *Quantity*. We sum up the rows in the newly created column and get a single number of the total purchased pieces.

```{r}
lego_df %>%
    select(Pieces, Quantity) %>%
    transmute(Total_Pieces = Pieces * Quantity) %>%
    summarize(sum(Total_Pieces, na.rm = TRUE))
```


###8. What state has spent the most money on legos? Hint - customer area codes may prove useful for this.

First we create a list of US area codes after some research. 
```{r}
area_code = list(
  Alaska = c(907),
  Alabama = c(205, 251, 256, 334),
  Arkansas = c(479, 501, 870),
  Arizona = c(480, 520, 602, 623, 928),
  California = c(209, 213, 310, 323, 408, 415, 510, 530, 559, 562, 619, 626, 650, 661, 707, 714, 760, 805, 818, 831, 858, 909, 916, 925, 949, 951),
  Colorado = c(303, 719, 970),
  Connecticut = c(203, 860),
  D.C = c(202),
  Delaware = c(302),
  Florida = c(239, 305, 321, 352, 386, 407, 561, 727, 772, 813, 850, 863, 904, 941, 954),
  Georgia = c(229, 404, 478, 706, 770, 912),
  Hawaii = c(808),
  Iowa = c(319, 515, 563, 641, 712),
  Idaho = c(208),
  Illinois = c(217, 309, 312, 618, 630, 708, 773, 815, 847),
  Indiana = c(219, 260, 317, 574, 765, 812),
  Kansas = c(316, 620, 785, 913),
  Kentucky = c(270, 502, 606, 859),
  Louisiana = c(225, 318, 337, 504, 985),
  Massachusetts = c(413, 508, 617, 781, 978),
  Maryland = c(201, 410),
  Maine = c(207),
  Michigan = c(231, 248, 269, 313, 517, 586, 616, 734, 810, 906, 989),
  Minnesota = c(218, 320, 507, 612, 651, 763, 952),
  Missouri = c(314, 417, 573, 636, 660, 816),
  Mississippi = c(228, 601, 662),
  Montana = c(406),
  North_Carolina = c(252, 336, 704, 828, 910, 919),
  North_Dakota = c(701),
  Nebraska = c(308, 402),
  New_Hampshire = c(603),
  New_Jersey = c(201, 609, 732, 856, 908, 973),
  New_Mexico = c(505, 575),
  Nevada = c(702, 775),
  New_York = c(212, 315, 516, 518, 585, 607, 631, 716, 718, 845, 914),
  Ohio = c(216, 330, 419, 440, 513, 614, 740, 937),
  Oklahoma = c(405, 580, 918),
  Oregon = c(503, 541),
  Pennsylvania = c(215, 412, 570, 610, 717, 724, 814),
  Rhode_Island = c(401),
  South_Carolina = c(803, 843, 864),
  South_Dakota = c(605),
  Tennessee = c(423, 615, 731, 865, 901, 931),
  Texas = c(210, 214, 254, 281, 325, 361, 409, 432, 512, 713, 806, 817, 830, 903, 915, 936, 940, 956, 972, 979),
  Utah = c(435, 801),
  Virginia = c(276, 434, 540, 703, 757, 804),
  Vermont = c(802),
  Washington = c(206, 253, 360, 425, 509),
  Wisconsin = c(262, 414, 608, 715, 920),
  West_Virginia = c(304),
  Wyoming = c(307) )

str(lego_df %>% select(phone_number))

```
